Constraints on the quasi-normal mode frequencies of the LIGO-Virgo signals by making full use of gravitational-wave modeling

### 2021-02-15 papers/intro_paper/discussion.tex
more conclusions

\comment{AB: I am sorry, but I had no time to write this section. Please write a first draft. I have read in the last week several papers
about extracting information on the nature of dark objects and gravity in the strong-field regime combining LIGO/Virgo and also
EHT. I wanted to refer to them --- for example Maggio et al., Volkel et al., Franciolini et al., Cano et al.
It is also good if we cite papers that have predicted QNMs in gravity theories alternative to GR. We did it in the paper with
Richard and Vivien.}

@@

These constraints could in principle be used to constrain specific non-GR theories and exotic compact objects.
\rb{this is taken from \paperone, needs to be updated:}QNM frequencies of spherically symmetric solutions were computed in theories such as Einstein-Maxwell-dilaton~\cite{Ferrari:2000ep}, dynamical Chern-Simons gravity~\cite{Molina:2010fb}, Einstein-dilaton-Gauss-Bonnet gravity~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk} and for some solutions in massive (bi)gravity~\cite{Brito:2013wya,Brito:2013yxa,Babichev:2015zub}. On
the other hand, not much progress has been made to compute QNMs for
spinning BHs in alternative theories to GR, the only exception
being the Kerr-Newman case in Einstein-Maxwell
theory~\cite{Pani:2013ija,Pani:2013wsa,Mark:2014aja,Dias:2015wqa}. Most
of the estimates for QNMs of spinning BHs in modified gravity have
instead used the connection between the light ring and
QNMs~\cite{Blazquez-Salcedo:2016enn,Glampedakis:2017dvb,Jai-akson:2017ldo,Glampedakis:2017cgd},
which is formally only valid in the eikonal $\ell \to \infty$ limit
and known to fail to describe some families of QNMs when additional
degrees of freedom are present~\cite{Blazquez-Salcedo:2016enn}.

To constrain the deviations from GR we decided to use the most generic and conservative parametrization, Eqs.~\eqref{eq:nongr_freqs_a} and~\eqref{eq:nongr_freqs_b}, where the fractional deviations $(\delta f_{\ell m0,\delta \tau_{\ell m0}$ are taken to be completely free parameters. In principle, this model can also be used with more restricted parametrizations, such as the one proposed in Ref.~\cite{Maselli:2019mjd} and recently applied on LIGO-Virgo events in Ref. ~\cite{Carullo:2021dui}, where deviations from the GR QNMs explicitly depend on a perturbative expansion in the BH spin and possible extra non-GR parameters. Other examples also include proposals to directly relate measurements of the QNM complex frequencies to non-GR parametrized BH metrics~\cite{Suvorov:2021amy,Volkel:2020daa} which, as proposed in ~\cite{Volkel:2020daa,Volkel:2020xlc} could be used jointly with constraints coming from the Event Horizon Telescope~\cite{Volkel:2020xlc,Psaltis:2020lvx}.

This work can be improved in several fronts... It could be easily extended to generic precessing waveforms. Interesting future studies include using this model using waveforms obtained in recent numerical relativity simulations of non-GR theories.

>>>>

@@

These constraints could in principle be used to constrain specific non-GR theories and exotic compact objects.
\rb{this is taken from \paperone, needs to be updated:}
QNM frequencies of spherically symmetric solutions were computed in theories such as Einstein-Maxwell-dilaton~\cite{Ferrari:2000ep}, dynamical Chern-Simons gravity~\cite{Molina:2010fb}, Einstein-dilaton-Gauss-Bonnet gravity~\cite{Pani:2009wy,Blazquez-Salcedo:2016enn,Blazquez-Salcedo:2017txk} and for some solutions in massive (bi)gravity~\cite{Brito:2013wya,Brito:2013yxa,Babichev:2015zub}. On
the other hand, not much progress has been made to compute QNMs for
spinning BHs in alternative theories to GR, the only exception
being the Kerr-Newman case in Einstein-Maxwell
theory~\cite{Pani:2013ija,Pani:2013wsa,Mark:2014aja,Dias:2015wqa}. Most
of the estimates for QNMs of spinning BHs in modified gravity have
instead used the connection between the light ring and
QNMs~\cite{Blazquez-Salcedo:2016enn,Glampedakis:2017dvb,Jai-akson:2017ldo,Glampedakis:2017cgd},
which is formally only valid in the eikonal $\ell \to \infty$ limit
and known to fail to describe some families of QNMs when additional
degrees of freedom are present~\cite{Blazquez-Salcedo:2016enn}.  
EFT~\cite{Franciolini:2018uyq,Cano:2020cao,Cardoso:2018ptl}, ECO~\cite{Maggio:2020jml}

To constrain the deviations from GR we decided to use the most generic and conservative parametrization, Eqs.~\eqref{eq:nongr_freqs_a} and~\eqref{eq:nongr_freqs_b}, where the fractional deviations $(\delta f_{\ell m0},\delta \tau_{\ell m0})$ are taken to be completely free parameters. In principle, this model can also be used with other, more restricted, parametrizations that could help to map constraints on the QNM complex frequencies to constraints in specific beyond-GR theories. This includes for example the parametrization proposed in Ref.~\cite{Maselli:2019mjd}, recently applied to LIGO-Virgo GW events in Ref. ~\cite{Carullo:2021dui}, where deviations from the GR QNMs explicitly depend on a perturbative expansion in the BH spin and possible extra non-GR parameters. Other examples also include proposals to write the deviations from GR in terms of a small parametrized deviations of the perturbation equations~\cite{Cardoso:2019mqo,McManus:2019ulj} or proposals to directly relate measurements of the QNM complex frequencies to non-GR parametrized BH metrics~\cite{Suvorov:2021amy,Volkel:2020daa}. As proposed in~\cite{Volkel:2020daa,Volkel:2020xlc} constraints on the BH metric using QNM measurements could then also be used jointly with constraints coming from the Event Horizon Telescope~\cite{Volkel:2020xlc,Psaltis:2020lvx}.

Generalization to generic precessing waveforms is straightforward and could be done using the recently developed model reported in Ref.~\cite{Ossokine:2020kjp}.

Finally, it would also be important to test our model against waveforms obtained with numerical relativity simulations of specific beyond-GR theories. Such simulations are however extremely challenging to do (when at all possible), and have so far only been done for a handful of theories, focusing mostly on proof-of-concept simulations~\cite{Healy:2011ef,Berti:2013gfa,Cao:2013osa,Okounkova:2017yby,Hirschmann:2017psw,Witek:2018dmd,Okounkova:2019dfo,Okounkova:2019zjf,Okounkova:2020rqw,East:2020hgw}. Nonetheless, given the recent efforts put forward in order to simulate BBHs in beyond-GR theories, we hope that accurate non-GR IMR waveforms will become available in the near future.
